---
title: "Nordnet ETF"
author: "Christian Kruse"
date: "2024-08-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
```

```{r}
pacman::p_load(tidyr,
               dplyr,
               ggplot2,
               scales,
               pROC,
               DT,
               lubridate,
               # XML,
               caret,
               quantmod,
               kableExtra,
               survival,
               survminer,
               caret,
               logger,
               # statsDK,
               # rentrez,
               parallel,
               foreach,
               pbmcapply,
               # earth,
               # progress,
               data.table,
               openxlsx
               # glue,
               # gganimate
               )

```

# Nordnet ETF

```{r}
filepath_nordnet = list.files(pattern = "fonde")
filepath_abis = list.files(pattern = "abis")
```

```{r}
df_abis = openxlsx::read.xlsx(filepath_abis) %>% 
  distinct(ISIN,
           `Navn.andelsklasse/Name.Shareclass`) %>% 
  dplyr::rename(Name=`Navn.andelsklasse/Name.Shareclass`)
```

```{r}
df_nordnet = read.csv(filepath_nordnet,sep = "\t", fileEncoding="UCS-2LE",colClasses = "character") %>% 
  dplyr::mutate(Antal.ejere=as.integer(gsub("\\.","",Antal.ejere)),
                Årlig.omk...=as.numeric(gsub(",",".",Årlig.omk...)),
                Ticker=paste0(Ticker,".DE")) %>% 
  dplyr::rename(Maanedsopsparing=Fås.i.Månedsopsparingen,
                Aarligeomkostninger=Årlig.omk...,
                Antalejere=Antal.ejere,
                ticker=Ticker) %>% 
  distinct(Navn,
           ticker,
           ISIN,
           Valuta,
           Udbyttepolitik,
           Aarligeomkostninger,
           Antalejere,
           Maanedsopsparing
           ) %>% 
  replace_na(list(Maanedsopsparing="Nej")) %>% 
  left_join(df_abis) %>% 
  dplyr::mutate(Positiv=ifelse(!is.na(Name),"Positivliste","-Positivliste")) %>% 
  # filter(Positiv=="Positivliste") %>% 
  arrange(desc(Antalejere))

```

# Abis

```{r}
df_abis %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

# Nordnet

```{r}
df_nordnet %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

# Nordnet - Positivliste

```{r}
df_nordnet %>% 
  filter(Positiv=="Positivliste")
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```
# Nordnet - Positivliste, Månedsopsparing

```{r}
df_nordnet %>% 
  filter(Positiv=="Positivliste",
         Maanedsopsparing=="Ja")
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

# Nordnet - %Positivliste, Månedsopsparing

```{r}
df_nordnet %>% 
  filter(!Positiv=="Positivliste",
         Maanedsopsparing=="Ja") %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


# Yahoo

## +Positivliste, +Månedsopsparing

```{r}
tickers_nordnet_pm = df_nordnet %>% 
  filter(Positiv=="Positivliste",
         Maanedsopsparing=="Ja") %>% 
  pull(ticker)
```

```{r}
tickers_nordnet_nm = df_nordnet %>% 
  filter(!Positiv=="Positivliste",
         Maanedsopsparing=="Ja") %>% 
  pull(ticker)
```

```{r}
tickers_nordnet_positiv = df_nordnet %>% 
  filter(Positiv=="Positivliste") %>% 
  pull(ticker)
```

```{r}
tickers_nordnet_negativ = df_nordnet %>% 
  filter(!Positiv=="Positivliste") %>% 
  pull(ticker)
```

```{r}
cores = min(detectCores(),40)
```

```{r}

query_yahoo = function(ticker) {
  getSymbols(ticker, env = NULL) %>% 
  as.data.frame(.) %>% 
  dplyr::mutate(Date=row.names(.)) %>% 
  dplyr::mutate(Date=gsub("X","",Date)) %>% 
  dplyr::mutate(Date=ymd(Date)) %>% 
  dplyr::select(c(7,1,2,3,4,5,6)) %>% 
  setNames(.,c("Date","Open","High","Low","Close","Volume","Adjusted")) %>% 
  na.omit() %>% 
  mutate(greenRed=ifelse(Open>Close,
                         "Red",
                         "Green")) %>% 
  dplyr::mutate(ticker=ticker) %>% 
  relocate(ticker) #%>% 
  # dplyr::mutate(SMA_180=TTR::SMA(x = Close,n = 365.25*0.5)) %>% 
  # dplyr::mutate(SMA_365=TTR::SMA(x = Close,n = 365.25*1)) %>% 
  # dplyr::mutate(SMA_730=TTR::SMA(x = Close,n = 365.25*2))
}
```

```{r}


df_ticker_data = pbmclapply( c(tickers_nordnet_pm,tickers_nordnet_nm) ,function(ticker) {
# df_ticker_data = lapply(tickers_shotgun,function(ticker) {
  Sys.sleep(round(runif(n = 1,min = 0,max = 20)))
  message(ticker)
  tryCatch(expr = {query_yahoo(ticker)},error=function(e) { data.frame() })
},mc.cores=cores)
df_ticker_data = do.call("rbind",df_ticker_data)

length(unique(df_ticker_data$ticker))
```

```{r}


df_nordnet %>% 
  inner_join( df_ticker_data ) %>% 
  filter(Volume>0) %>% 
  group_by(Positiv,ticker,Navn) %>% 
  top_n(n = 30,wt = Date) %>% 
  dplyr::summarize(Volume=mean(Volume)) %>% 
  arrange(Positiv,desc(Volume)) %>% 
  group_by(Positiv) %>% 
  top_n(n=100,wt = Volume) %>% 
  dplyr::mutate(rang=rev(rank(Volume))) %>% 
  dplyr::mutate(Navn=paste0(Navn," ( ",ticker," , ",scales::number(round(Volume/100000),big.mark=",")," hk)")) %>% 
  dplyr::select(-Volume,-ticker) %>% 
  spread(Positiv,Navn)
  
```

## Stats


```{r}

df_ticker_data_tickers = df_ticker_data %>% distinct(ticker)
df_ticker_data_tickers = split(df_ticker_data_tickers,unique(df_ticker_data_tickers$ticker))

fit_ticker_data = do.call("rbind",pbmclapply( df_ticker_data_tickers, function(ticker_row) {
  
  data = df_ticker_data %>% inner_join(ticker_row) %>% filter(min(Date)<=Sys.Date()-years(1))
  fit_lm = lm(Close~Date,data=data)
  fit_log = lm(log(Close)~Date,data=data)
  # LM
  fit_lm_rsq = summary(fit_lm)$r.squared
  fit_lm_yrly = predict(fit_lm,data.frame(Date=Sys.Date()))/predict(fit_lm,data.frame(Date=Sys.Date()-years(1)))-1
  # LOG
  fit_log_rsq = summary(fit_log)$r.squared
  fit_log_yrly = predict(fit_log,data.frame(Date=Sys.Date()))/predict(fit_log,data.frame(Date=Sys.Date()-years(1)))-1
  
  return(
    ticker_row %>% 
      dplyr::mutate(fit_lm_rsq=fit_lm_rsq,
                    fit_log_rsq=fit_log_rsq,
                    fit_lm_yrly=fit_lm_yrly,
                    fit_log_yrly=fit_log_yrly
                    )
  )
  
},mc.cores = cores))


fit_ticker_data

```


```{r eval=F}
df_ticker_stats = df_ticker_data %>% 
  group_by(ticker) %>% 
  filter(Date>=Sys.Date()-years(5)) %>% 
  filter(n()>180) %>% 
  dplyr::mutate(mean_=mean(Close),
                sd_=sd(Close)) %>% 
  dplyr::mutate(pct=pnorm(Close,mean_,sd_),
                rsi_30=TTR::RSI(Close,30),
                macd_macd=TTR::MACD(Close)[,1],
                macd_signal=TTR::MACD(Close)[,2]) %>% 
  filter(Date==max(Date)) %>% 
  arrange((rsi_30)) %>% 
  distinct(ticker,
           Date,
           pct,
           rsi_30,
           macd_macd,
           macd_signal) %>% 
  ungroup()


```


```{r eval=F}
df_ticker_stats %>% 
  inner_join(df_positiv_maanedsopsparing) %>% 
  relocate(ticker,
           Name,
           Aarligeomkostninger,
           Antalejere) %>% 
  ggplot(.,aes(x=pct,y=rsi_30,color=ticker)) +
  geom_point() +
  theme(legend.position="null")
```

```{r eval=F}
df_ticker_stats %>% 
  inner_join(df_positiv_maanedsopsparing) %>% 
  relocate(ticker,
           Name,
           Aarligeomkostninger,
           Antalejere) %>% 
  ggplot(.,aes(x=Antalejere,y=Aarligeomkostninger,color=ticker)) +
  geom_point() +
  theme(legend.position="null")
```



## Predict increase

### Outcomes

```{r eval=F}
find_increase = function(data) {
  # print(data)
  first_value = data[1]
  incr_value = first_value*1.10
  which(data>=incr_value)[1]
}

find_chg_abs = function(data) {
  # print(data)
  first_value = data[1]
  incr_value = tail(data,1)
  100*(first_value/incr_value-1)
}

find_decrease = function(data) {
  # print(data)
  first_value = data[1]
  decr_value = first_value*0.9
  which(data<=decr_value)[1]
}
```

```{r eval=F}
df_cox = df_ticker_data %>% 
  group_by(ticker) %>% 
  filter(n()>200) %>% 
  dplyr::mutate(eofu_chg=rollapply(data = Close, 365, find_chg_abs,fill=NA,align="right")) %>% 
  dplyr::mutate(eofu_time_incr=rollapply(data = Close, 365, find_increase,fill=NA,align="right")) %>% 
  dplyr::mutate(eofu_time_decr=rollapply(data = Close, 365, find_decrease,fill=NA,align="right")) %>% 
  tail(-100) %>%
  dplyr::mutate(eofu_bool_incr=ifelse(is.na(eofu_time_incr),0,1)) %>% 
  dplyr::mutate(eofu_bool_decr=ifelse(is.na(eofu_time_decr),0,1)) %>% 
  replace_na(list(eofu_time_incr=365,eofu_time_decr=365))
```

Proportions of outcomes:

Increases:

```{r eval=F}
prop.table( table(df_cox$eofu_bool_incr) )
```

Decreases:

```{r eval=F}
prop.table( table(df_cox$eofu_bool_decr) )
```

```{r eval=F}
fit_surv_cox_incr = survfit(Surv(eofu_time_incr,eofu_bool_incr)~1 ,data=df_cox) 
ggsurvplot(fit = fit_surv_cox_incr,data = df_cox,conf.int = T,surv.median.line = "hv")
```

```{r eval=F}
fit_surv_cox_decr = survfit(Surv(eofu_time_decr,eofu_bool_decr)~1 ,data=df_cox) 
ggsurvplot(fit = fit_surv_cox_decr,data = df_cox,conf.int = T,surv.median.line = "hv")
```
## Map covariates to risk/change on increase

First calculate all the different predictors at different time for use in later modelling.

```{r eval=F}

df_grid = expand.grid(ticker=unique(df_cox$ticker),
                      frequency=seq(7,101,by=20))
df_grid = split(df_grid,seq(nrow(df_grid)))

df_cox_risk_factors = do.call("rbind",pbmclapply(df_grid,function(grid) {
  
  return(
    tryCatch(expr={
  df_cox %>% 
    filter(ticker==grid$ticker) %>% 
    filter(n()>200) %>% 
    arrange(desc(Date)) %>% 
    dplyr::mutate(rsi=TTR::RSI(Close,na.rm=T),
                  smax200=TTR::SMA(Close,n=grid$frequency)-TTR::SMA(Close,n=200),
                  macdosc=TTR::MACD(Close,nFast=grid$frequency,nSlow=grid$frequency*2,nSig=floor(grid$frequency*(2/3)))[,1],
                  macdsignal=TTR::MACD(Close,nFast=grid$frequency,nSlow=grid$frequency*2,nSig=floor(grid$frequency*(2/3)))[,2],
                  macdoscsignal=TTR::MACD(Close,nFast=grid$frequency,nSlow=grid$frequency*2,nSig=floor(grid$frequency*(2/3)))[,1]-TTR::MACD(Close,nFast=grid$frequency,nSlow=grid$frequency*2,nSig=floor(grid$frequency*(2/3)))[,2],
                  bbandspctb=TTR::BBands(Close,grid$frequency)[,4],
                  cci=TTR::CCI(Close,grid$frequency)[,1],
                  momentum=TTR::momentum(Close,grid$frequency),
                  # pct=pnorm(Close,mean=mean(Close),sd=sd(Close)),
                  # adx=TTR::ADX(value)[,3],
                  cmo=TTR::CMO(Close,grid$frequency),
                  gainpctxdays=100*((Close/lag(Close,grid$frequency))-1)) %>% 
    dplyr::select(ticker,
                  Date,
                  eofu_chg,
                  eofu_bool_incr,
                  eofu_time_incr,
                  eofu_bool_decr,
                  eofu_time_decr,
                  rsi:gainpctxdays) %>% 
    gather(stat,val,rsi:gainpctx_days) %>% 
    dplyr::mutate(stat=paste0(stat,"_",grid$frequency)) %>% 
    na.omit() %>% 
    ungroup()
    },error=function(e) {data.frame()})
  )
  
},mc.cores=50))

```


Then model

```{r eval=F}
rows = df_cox_risk_factors %>% distinct(ticker,stat)
rows = split(rows,seq(nrow(rows)))

df_cox_analysis = do.call("rbind",pbmclapply(rows,function(grid) {
  
  return(
    tryCatch(expr={
      
          temp_df = df_cox_risk_factors %>% 
            inner_join(grid)
          # fit_temp = coxph(Surv(eofu_time_incr,eofu_bool_incr) ~ val , data=temp_df )
          fit_temp = coxph(Surv(eofu_time_incr,eofu_bool_incr) ~ pspline(val,df = 2) , data=temp_df )
          fit_concordance = concordance( Surv(eofu_time_incr,eofu_bool_incr) ~ predict(fit_temp, temp_df), temp_df)
          term_plot = termplot(fit_temp,se=TRUE,plot=FALSE)$val
          return(term_plot %>% dplyr::mutate(ticker=grid$ticker,
                                             df=2,
                                             var=grid$stat,
                                             c_index=fit_concordance$concordance)
                 )
      
    },error=function(e) {data.frame()})
  )
  
},mc.cores=50))

df_cox_analysis %>% 
  separate(var,into=c("metric","time")) %>% 
  ggplot(.,aes(x=metric,y=c_index,color=time)) +
  geom_point()

```

```{r eval=F}
df_cox_analysis %>% 
  ggplot(.,aes(x=x,y=y,color=ticker)) +
  geom_line() +
  facet_wrap(~var,scales="free")
```


### Covariates

```{r eval=F}

lm_coefs = function(data) {
  # print(data)
  lm_exp = lm(log(value)~date,data=data.frame(date=seq(1,14,by=1),value=data))
  lm_lin = lm(value~date,data=data.frame(date=seq(1,14,by=1),value=data))
  return( data.frame(lin_coef_14=summary(lm_lin)$coefficients[2,1],
                     lin_rsq_14=summary(lm_lin)$r.squared,
                     exp_coef_14=exp(summary(lm_exp)$coefficients[2,1] ),
                     exp_rsq_14=summary(lm_exp)$r.squared ) )
}

# df_covariate_r2_lm = df_macro_yahoo %>% 
#   group_by(series_id) %>% 
#   # head(10000) %>% 
#   filter(n()>200) %>% 
#   dplyr::mutate(coef=rollapply(data = value, 14, lm_coefs,fill=NA,align="right")) %>% 
#   pull(coef) %>% 
#   data.frame() %>% 
#   setNames(.,c("lin_coef_14","lin_rsq_14","exp_coef_14","exp_rsq_14"))


  # bind_cols(df_covariate_r2_lm)
 
```



```{r eval=F}
fit_params %>% 
  # filter(y>0) %>% 
  ggplot(.,aes(x=x,y=y,fill=var,ymin=lwr,ymax=upr)) +
  geom_line() +
  geom_ribbon() +
  facet_wrap(~var,scales="free") +
  geom_hline(yintercept = 0,linetype=2) +
  geom_vline(xintercept = 0,linetype=2)
```

```{r eval=F}
fit_params %>% 
  # filter(y>0) %>% 
  ggplot(.,aes(x=x,y=exp(y),fill=var,ymin=exp(lwr),ymax=exp(upr))) +
  geom_line() +
  geom_ribbon() +
  facet_wrap(~var,scales="free") +
  geom_hline(yintercept = 0,linetype=2) +
  geom_vline(xintercept = 0,linetype=2)
```


Concordance:

```{r eval=F}
fit_params %>% distinct(var,df,c_index) %>% arrange(desc(c_index)) %>%  kable()
```

### Combined models



```{r eval=F}

df_combined_cox = df_cox_risk_factors %>% 
  filter(stat %in% c("rsi_7","macdsignal")) %>% 
  distinct(ticker,
           Date,
           eofu_bool_incr,
           eofu_time_incr,
           stat,
           val) %>% 
  spread(stat,val) %>% 
  dplyr::select(-ticker,-Date)

fit_temp = coxph(Surv(eofu_time_incr,eofu_bool_incr) ~ pspline(rsi_7,2),
                 data= df_combined_cox)

library(MASS)
fit_temp_aic = stepAIC(fit_temp)
fit_temp_aic
fit_concordance = concordance( Surv(eofu_time_incr,eofu_bool_incr) ~ predict(fit_temp, df_combined_cox), df_combined_cox)
termplot(fit_temp,se=FALSE,plot=TRUE)
```


## Cox

```{r eval=F}

fit_coxph_incr = coxph(Surv(eofu_time_incr,eofu_bool_incr)~ rsi_14 + sma50_200 + macd_osc + macd_signal + macd_osc_signal + bbands_pctb + cci + momentum + pct,
                  data=df_model )
fit_coxph_incr = MASS::stepAIC(fit_coxph_incr)

fit_coxph_decr = coxph(Surv(eofu_time_decr,eofu_bool_decr)~ rsi_14 + sma50_200 + macd_osc + macd_signal + macd_osc_signal + bbands_pctb + cci + momentum + pct,
                  data=df_model )
fit_coxph_decr = MASS::stepAIC(fit_coxph_decr)

fit_coxph_incr$concordance
fit_coxph_decr$concordance

```


```{r eval=F}
summary(fit_coxph_incr)$coefficients %>% 
  data.frame() %>% 
  dplyr::select(2) %>% 
  setNames(.,"exp_coef") %>% 
  arrange(desc(exp_coef))
```

```{r eval=F}
summary(fit_coxph_decr)$coefficients %>% 
  data.frame() %>% 
  dplyr::select(2) %>% 
  setNames(.,"exp_coef") %>% 
  arrange(desc(exp_coef))
```


# Testing

```{r eval=F}
df_testing = df_model %>% 
  ungroup() %>% 
  dplyr::mutate(relative_risk_incr=predict(fit_coxph_incr,.,type="risk")) %>%
  dplyr::mutate(relative_risk_decr=predict(fit_coxph_decr,.,type="risk")) %>%
  dplyr::mutate(rel_risk=relative_risk_incr/relative_risk_decr) %>% 
  dplyr::select(relative_risk_incr,relative_risk_decr,rel_risk,eofu_bool_incr,eofu_bool_decr)
```

## Above cutoff

```{r eval=F}
# Incr and Decr from relative_risk_incr
df_cutoff_relative_risk_incr = do.call("rbind",lapply(c(0,0.25,0.5,0.75,seq(1,30,by=1)),function(cutoff) {
  
  df_testing %>% 
    filter(relative_risk_incr>=cutoff) %>% 
    dplyr::summarize(tpr=sum(eofu_bool_incr)/nrow(.),
                     fpr=sum(eofu_bool_decr)/nrow(.)) %>% 
    ungroup() %>% 
    dplyr::mutate(cutoff=cutoff)
  
}))

df_cutoff_relative_risk_incr %>% 
  dplyr::mutate(diff=tpr-fpr) %>% 
  ggplot(.,aes(x=cutoff,y=tpr)) +
  geom_line() +
  geom_line(aes(x=cutoff,y=fpr)) +
  geom_line(aes(x=cutoff,y=diff),color="lightsteelblue")
```


```{r eval=F}
# Incr and Decr from relative_risk_decr
df_cutoff_relative_risk_decr = do.call("rbind",lapply(c(0,0.25,0.5,0.75,seq(1,300,by=1)),function(cutoff) {
  
  df_testing %>% 
    filter(relative_risk_decr>=cutoff) %>% 
    dplyr::summarize(tpr=sum(eofu_bool_decr)/nrow(.),
                     fpr=sum(eofu_bool_incr)/nrow(.)) %>% 
    ungroup() %>% 
    dplyr::mutate(cutoff=cutoff)
  
}))

df_cutoff_relative_risk_decr %>% 
  dplyr::mutate(diff=tpr-fpr) %>% 
  ggplot(.,aes(x=cutoff,y=tpr)) +
  geom_line() +
  geom_line(aes(x=cutoff,y=fpr)) +
  geom_line(aes(x=cutoff,y=diff),color="lightsteelblue")

```

## Below cutoff

```{r eval=F}
# Incr and Decr from relative_risk_incr
do.call("rbind",lapply(c(0,0.25,0.5,0.75,seq(1,30,by=1)),function(cutoff) {
  
  df_testing %>% 
    filter(relative_risk_incr<=cutoff) %>% 
    dplyr::summarize(tpr=sum(eofu_bool_decr==0)/nrow(.),
                     fpr=sum(eofu_bool_incr==0)/nrow(.)) %>% 
    ungroup() %>% 
    dplyr::mutate(cutoff=cutoff)
  
})) %>% 
  dplyr::mutate(diff=tpr-fpr) %>% 
  ggplot(.,aes(x=cutoff,y=tpr)) +
  geom_line() +
  geom_line(aes(x=cutoff,y=fpr)) +
  geom_line(aes(x=cutoff,y=diff),color="lightsteelblue")
```


```{r eval=F}
# Incr and Decr from relative_risk_decr
do.call("rbind",lapply(c(0,0.25,0.5,0.75,seq(1,300,by=1)),function(cutoff) {
  
  df_testing %>% 
    filter(relative_risk_decr<=cutoff) %>% 
    dplyr::summarize(tpr=sum(eofu_bool_decr==0)/nrow(.),
                     fpr=sum(eofu_bool_incr==0)/nrow(.)) %>% 
    ungroup() %>% 
    dplyr::mutate(cutoff=cutoff)
  
})) %>% 
  dplyr::mutate(diff=tpr-fpr) %>% 
  ggplot(.,aes(x=cutoff,y=tpr)) +
  geom_line() +
  geom_line(aes(x=cutoff,y=fpr)) +
  geom_line(aes(x=cutoff,y=diff),color="lightsteelblue")

```


```{r eval=F}
df_testing %>% 
  group_by(relative_risk_incr_cut) %>% 
  dplyr::summarize(freq_true=sum(eofu_bool_incr)/n(),
                   freq_false=sum(eofu_bool_incr==0)/n()) %>% 
  gather(stat,val,freq_true:freq_false) %>% 
  ggplot(.,aes(x=relative_risk_incr_cut,y=val,fill=stat)) +
  geom_col()

df_testing %>% 
  group_by(relative_risk_decr_cut) %>%  
  dplyr::summarize(freq_true=sum(eofu_bool_incr)/n(),
                   freq_false=sum(eofu_bool_incr==0)/n()) %>% 
  gather(stat,val,freq_true:freq_false) %>% 
  ggplot(.,aes(x=relative_risk_decr_cut,y=val,fill=stat)) +
  geom_col()

```

```{r eval=F}
roc_incr = pROC::roc(predictor=df_testing$relative_risk_incr,response=df_testing$eofu_bool_incr)
best_incr = coords(roc_incr,x="best",best.method="youden")$threshold
coords(roc_incr) %>% 
  sample_n(10000) %>% 
  gather(stat,val,specificity:sensitivity) %>% 
  filter(threshold<20) %>% 
  ggplot(.,aes(x=threshold,y=val,color=stat)) +
  geom_line()
```


```{r eval=F}
roc_decr = pROC::roc(predictor=df_testing$relative_risk_decr,response=df_testing$eofu_bool_decr)
best_decr = coords(roc_decr,x="best",best.method="youden")$threshold
coords(roc_decr) %>% 
  sample_n(10000) %>% 
  gather(stat,val,specificity:sensitivity) %>% 
  filter(threshold<10) %>% 
  ggplot(.,aes(x=threshold,y=val,color=stat)) +
  geom_line()
```

# Prediction going forward

```{r eval=F}

# Extra trading day with 5% drop
# df_extra_day = df_ticker_data %>% 
#   group_by(ticker) %>% 
#   filter(n()>200) %>% 
#   filter(Date==max(Date,na.rm=T)) %>% 
#   dplyr::mutate(Date=Date+days(1),
#                 Close=Close*0.95)

# Re-calc
df_covariate_r2_lm = df_ticker_data %>% 
  group_by(ticker) %>% 
  # head(10000) %>% 
  filter(n()>200) %>% 
  # bind_rows(df_extra_day) %>% 
  dplyr::mutate(coef=rollapply(data = Close, 14, lm_coefs,fill=NA,align="right")) %>% 
  pull(coef) %>% 
  data.frame() %>% 
  setNames(.,c("lin_coef_14","lin_rsq_14","exp_coef_14","exp_rsq_14"))

df_covariates = df_ticker_data %>% 
  group_by(ticker) %>% 
  filter(n()>200) %>% 
  # bind_rows(df_extra_day) %>% 
  dplyr::mutate(rsi_14=TTR::RSI(Close,na.rm=T),
                sma50_200=TTR::SMA(Close,n=50)-TTR::SMA(Close,n=200),
                macd_osc=TTR::MACD(Close)[,1],
                macd_signal=TTR::MACD(Close)[,2],
                macd_osc_signal=TTR::MACD(Close)[,1]-TTR::MACD(Close)[,2],
                bbands_pctb=TTR::BBands(Close)[,4],
                cci=TTR::CCI(Close)[,1],
                momentum=TTR::momentum(Close),
                pct=pnorm(Close,mean=mean(Close),sd=sd(Close)),
                # adx=TTR::ADX(value)[,3],
                cmo=TTR::CMO(Close),
                gain_pct_30_days=100*((Close/lag(Close,30))-1)) %>% 
  bind_cols( df_covariate_r2_lm ) %>% 
  dplyr::select(-Open,-High,-Low,-Close,-Volume,-Adjusted,-greenRed)

# Prediction
df_predict = df_ticker_data %>% 
  group_by(ticker) %>% 
  filter(n()>200) %>% 
  top_n(n = 2,wt=Date) %>% 
  ungroup() %>% 
  inner_join(df_covariates) %>% 
  arrange(ticker,Date) %>% 
  dplyr::mutate(relative_risk_incr=predict(fit_coxph_incr,.,type="risk")) %>%
  dplyr::mutate(relative_risk_decr=predict(fit_coxph_decr,.,type="risk")) %>%
  dplyr::mutate(rel_risk=relative_risk_incr/relative_risk_decr) %>%
  arrange(desc(rel_risk))
```


```{r eval=F}
order_ = df_predict %>% group_by(ticker) %>% filter(Date==max(Date)) %>% arrange(relative_risk_incr) %>% pull(ticker)
df_predict %>% 
  dplyr::mutate(cutoff=cut(relative_risk_incr,breaks=c(0,0.25,0.5,0.75,seq(1,50,by=1)))) %>% 
  inner_join(df_cutoff_relative_risk_incr %>% 
               dplyr::mutate(cutoff=cut(cutoff,breaks=c(0,0.25,0.5,0.75,seq(1,50,by=1))))) %>% 
  dplyr::mutate(Date=factor(Date),
                ticker=factor(ticker,levels=order_),
                label_=paste0(scales::percent(tpr,1)," / ",scales::percent(fpr,1))) %>% 
  dplyr::mutate(relative_risk_incr=log(relative_risk_incr)) %>% 
  ggplot(.,aes(x=ticker,y=relative_risk_incr,color=Date)) +
  geom_point() +
  geom_text(aes(label=label_)) +
  coord_flip()
```

```{r eval=F}

library(rPref)
library(ggrepel)
psel = high(relative_risk_incr) * low(relative_risk_decr)

psel(df_predict %>% group_by(ticker) %>% filter(Date==max(Date)) %>% ungroup(), psel,top=100) %>% 
  filter(.level<=3) %>% 
  filter(relative_risk_decr<2) %>% 
  dplyr::mutate(.level=factor(.level)) %>% 
  ggplot(.,aes(x=relative_risk_decr,y=relative_risk_incr,color=.level)) +
  geom_line() +
  geom_point(aes(size=rel_risk)) +
  geom_hline(yintercept = best_incr,linetype=2) +
  geom_vline(xintercept = best_decr,linetype=2) +
  ggrepel::geom_text_repel(aes(label=ticker))# +
  # scale_x_continuous(limits=c(0,2)) +
# scale_x_log10()

top_tickers = psel(df_predict %>% group_by(ticker) %>% filter(Date==max(Date)) %>% ungroup, psel, top = 100) %>% 
  filter(.level==1) %>% 
  pull(ticker)
```

```{r eval=F}

psel(df_predict %>% group_by(ticker) %>% filter(Date==max(Date)) %>% ungroup(), psel,top=100) %>% 
  filter(.level==1) %>% 
  filter(relative_risk_decr<2) %>% 
  arrange(desc(relative_risk_incr))
```


## Development over time


```{r eval=F}

# Re-calc
df_covariate_r2_lm = df_ticker_data %>% 
  filter(ticker %in% top_tickers) %>% 
  group_by(ticker) %>% 
  filter(n()>200) %>% 
  # bind_rows(df_extra_day) %>% 
  dplyr::mutate(coef=rollapply(data = Close, 14, lm_coefs,fill=NA,align="right")) %>% 
  pull(coef) %>% 
  data.frame() %>% 
  setNames(.,c("lin_coef_14","lin_rsq_14","exp_coef_14","exp_rsq_14"))

df_covariates = df_ticker_data %>% 
  filter(ticker %in% top_tickers) %>% 
  group_by(ticker) %>% 
  filter(n()>200) %>% 
  # bind_rows(df_extra_day) %>% 
  dplyr::mutate(rsi_14=TTR::RSI(Close,na.rm=T),
                sma50_200=TTR::SMA(Close,n=50)-TTR::SMA(Close,n=200),
                macd_osc=TTR::MACD(Close)[,1],
                macd_signal=TTR::MACD(Close)[,2],
                macd_osc_signal=TTR::MACD(Close)[,1]-TTR::MACD(Close)[,2],
                bbands_pctb=TTR::BBands(Close)[,4],
                cci=TTR::CCI(Close)[,1],
                momentum=TTR::momentum(Close),
                pct=pnorm(Close,mean=mean(Close),sd=sd(Close)),
                # adx=TTR::ADX(value)[,3],
                cmo=TTR::CMO(Close),
                gain_pct_30_days=100*((Close/lag(Close,30))-1)) %>% 
  bind_cols( df_covariate_r2_lm ) %>%
  filter(ticker %in% top_tickers) %>% 
  group_by(ticker) %>% 
  ungroup() %>% 
  arrange(ticker,Date) %>% 
  dplyr::mutate(relative_risk_incr=predict(fit_coxph_incr,.,type="risk")) %>%
  dplyr::mutate(relative_risk_decr=predict(fit_coxph_decr,.,type="risk")) %>%
  dplyr::mutate(rel_risk=relative_risk_incr/relative_risk_decr)
```


```{r eval=F}
df_covariates %>% 
  filter(ticker %in% top_tickers) %>% 
  filter(Date>=ymd("2024-01-01")) %>% 
  distinct(ticker,
           Date,
           # Close,
           relative_risk_incr,
           relative_risk_decr#,
           #rel_risk
           ) %>% 
  gather(stat,val,c(3:ncol(.))) %>% 
  ggplot(.,aes(x=Date,y=val,color=ticker)) +
  geom_line() +
  facet_wrap(~stat,scales="free_y",ncol=1)

```


# Månedsopsparing

```{r eval=F,fig.width=20,fig.height=10}

psel(df_predict %>% group_by(ticker) %>% filter(Date==max(Date)) %>% ungroup, psel, top = 100) %>% 
  inner_join( df_nordnet ) %>% 
  filter(Maanedsopsparing=="Ja") %>% 
  filter(.level<=5) %>% 
  distinct(ticker,
           Navn,
           relative_risk_incr,
           relative_risk_decr,
           rsi_14,
           macd_signal,
           cci,
           momentum,
           pct,
           gain_pct_30_days,
           exp_rsq_14,
           .level) %>% 
  dplyr::mutate(ticker=paste0(Navn,"\n(",ticker,")")) %>% 
  dplyr::mutate(ticker=forcats::fct_reorder(ticker,.level)) %>% 
  gather(stat,val,relative_risk_incr:.level) %>% 
  group_by(stat) %>% 
  dplyr::mutate(val_scaled=scales::rescale(val)) %>% 
  ggplot(.,aes(x=ticker,y=stat,fill=val_scaled)) +
  geom_tile() +
  theme(axis.text.x=element_text(angle=30,hjust=1)) +
  geom_text(aes(label=scales::number(val,accuracy = 0.01)),color="white")
```


# Uden for månedsopsparing, men positivlisten

```{r eval=F,fig.width=20,fig.height=10}

psel(df_predict %>% group_by(ticker) %>% filter(Date==max(Date)) %>% ungroup, psel, top = nrow(df_predict)) %>% 
  inner_join( df_nordnet ) %>% 
  inner_join( df_abis) %>% 
  filter(Maanedsopsparing=="Nej") %>% 
  filter(.level<=2) %>% 
  distinct(ticker,
           Navn,
           relative_risk_incr,
           relative_risk_decr,
           rsi_14,
           macd_signal,
           cci,
           momentum,
           pct,
           gain_pct_30_days,
           exp_rsq_14,
           .level) %>% 
  dplyr::mutate(ticker=paste0(Navn,"\n(",ticker,")")) %>% 
  dplyr::mutate(ticker=forcats::fct_reorder(ticker,.level)) %>% 
  gather(stat,val,relative_risk_incr:.level) %>% 
  group_by(stat) %>% 
  dplyr::mutate(val_scaled=scales::rescale(val)) %>% 
  ggplot(.,aes(x=ticker,y=stat,fill=val_scaled)) +
  geom_tile() +
  theme(axis.text.x=element_text(angle=30,hjust=1)) +
  geom_text(aes(label=scales::number(val,accuracy = 0.01)),color="white")
```

